### 2016-09-30 GBF-correctness-private-M.tex
added note for Jon about RO usage in the correctness game

%\section{Proof of Theorem~\ref{thm:bf-correctness}}
%\label{sec:thm3_fp}
\begin{proof}[Theorem~\ref{thm:bf-correctness}]
We use a game playing argument, please refer to Figures~\ref{fig:bf-correctness-games1} and~\ref{fig:bf-correctness-games2}. In $\game{0}$, the $\Hash$ does lazy sampling of elements from $[m]$ to mimic a random oracle(RO). For every distinct query, $\Hash$ returns a random value sampled from $[m]$. Here, the adversary $A$, along with $\Rep$ and $\Qry$ are given access to $\Hash$. It can be seen that, $\game{0}$ exactly simulates the correctness game of $\setprim_{\mathrm{Bloom}}$. So, $\AdvCorrect{\setprim_{\mathrm{Bloom}},r}{A} = \Prob{\game{0}(A) = 1}$.

$\game{1}$ is exactly same as $\game{0}$ except the $\Qry$ oracle is replaced by the code of $\Qry$, whereas in $\game{2}$, the $\Test$ oracle returns the hash values back to the adversary along with output of the $\Qry$ oracle. $\game{3}$ on the other hand, returns all the $k$ hash values for any query. This results in adversary getting $(k-1)$ hash values for free as we charge the adversary for a single query. Since $k$ is likely to be very small compared to the number of queries the adversary makes, this would not affect the analysis in any significant manner. Also, in real world, RO will be a hash function; hence the adversary can perform local computations to get the hash values. It can be easily seen that the output of all the games will be same. So, $\Prob{\game{0}(A) = 1} = \Prob{\game{1}(A) = 1} = \Prob{\game{2}(A) = 1} = \Prob{\game{3}(A) = 1}$.

@@

To summarize, 
\[
\AdvCorrect{\setprim_{\mathrm{Bloom}},r}{A} \leq  {\dbinom{q_T + q_H}{r}} \left( (1-e^{-kn/m})^k + O(1/n) \right)^r\,.
\]
which is the bound claimed in the theorem statement.
\begin{figure}[tp]
\fpage{.95}{
\hpagessl{.5}{.5}
{
\underline{$\game{0}(A)$}\\
$S \getsr A$; $\calC \gets \emptyset$; $\err \gets 0$\\
$(\pubaux,\privaux) \getsr \Rep^{\HashOracle}(S)$\\
$\bot \getsr A^{\TestOracle}(\pubaux)$\\
if $\err  < r$ then Return 0\\
Return 1\\

\oracle{$\TestOracle(\qry_x)$}\\
if $x \in \mathcal{C}$ then Return $\bot$\\
$\calC \gets \calC \cup x$\\
$a \gets \Qry^{\HashOracle}(\pubaux,\privaux, x)$\\
if $a \neq \qry_x(S)$ then \\
\nudge $\err \gets \err + 1$\\
Return~$a$\\

\oracle{$\HashOracle(i,\qry_y)$}\\
$v \getsr [m]$\\
if $T[i,y] \neq \undefined$\\
\nudge $v \gets T[i,y]$\\
$T[i,y] \gets v$\\
Ret $v$
}
{
\underline{$\game{1}(A)$}\\
$S \getsr A$; $\calC \gets \emptyset$; $\err \gets 0$\\
$(\pubaux,\privaux) \getsr \Rep^{\HashOracle}(S)$\\
$\bot \getsr A^{\TestOracle}(\pubaux)$\\
if $\err  < r$ then Return 0\\
Return 1\\

\oracle{$\TestOracle(\qry_x)$}\\
if $x \in \mathcal{C}$ then Return $\bot$\\
$\calC \gets \calC \cup x$; $M \gets\privaux$\\
for $j \in \{1,2,\ldots,k\}$\\
\nudge $h_j \gets \HashOracle(j, x)$\\
$x' \gets M[h_1] \xor M[h_2] \xor \ldots \xor M[h_k]$\\
if $x' \neq x$ then Return 0\\
$\err \gets \err + 1$\\
Return 1\\

\oracle{$\HashOracle(i,\qry_y)$}\\
$v \getsr [m]$\\
if $T[i,y] \neq \undefined$\\
\nudge $v \gets T[i,y]$\\
$T[i,y] \gets v$\\
Ret $v$
}
}
\fpage{.95}{
\hpagessl{.5}{.5}
{
\underline{$\game{2}(A)$}\\
$S \getsr A$; $\calC \gets \emptyset$; $\err \gets 0$\\
$(\pubaux,\privaux) \getsr \Rep^{\HashOracle}(S)$\\
$\bot \getsr A^{\TestOracle}(\pubaux)$\\
if $\err  < r$ then Return 0\\
Return 1\\

\oracle{$\TestOracle(\qry_x)$}\\
if $x \in \mathcal{C}$ then Return $\bot$\\
$\calC \gets \calC \cup x$; $M \gets\privaux$\\
for $j \in \{1,2,\ldots,k\}$\\
\nudge $h_j \gets \HashOracle(j, x)$\\
$x' \gets M[h_1] \xor M[h_2] \xor \ldots \xor M[h_k]$\\
if $x' \neq x$ then Return $(0, (h_1, \ldots, h_j))$ \\
$\err \gets \err + 1$\\
Return $(1, (h_1, \ldots, h_{k}) )$ \\

\oracle{$\HashOracle(i,\qry_y)$}\\
$v \getsr [m]$\\
if $T[i,y] \neq \undefined$\\
\nudge $v \gets T[i,y]$\\
$T[i,y] \gets v$\\
Ret $v$
}
{
\underline{$\game{3}(A)$}\\
$S \getsr A$; $\calC \gets \emptyset$; $\err \gets 0$\\
$(\pubaux,\privaux) \getsr \Rep^{\HashOracle}(S)$\\
$\bot \getsr A^{\TestOracle}(\pubaux)$\\
if $\err  < r$ then Return 0\\
Return 1\\

\oracle{$\TestOracle(\qry_x)$}\\
if $x \in \mathcal{C}$ then Return $\bot$\\
$\calC \gets \calC \cup x$; $M \gets\privaux$\\
$(h_1, \ldots, h_{k}) \gets \HashOracle(x)$\\
$x' \gets M[h_1] \xor M[h_2] \xor \ldots \xor M[h_k]$\\
if $x' \neq x$ then Return $(0, (h_1, \ldots, h_j))$ \\
$\err \gets \err + 1$\\
Return $(1, (h_1, \ldots, h_{k}) )$ \\

@@

\oracle{$\TestOracle(\qry_x)$}\\
if $x \in \mathcal{C}$ then Return $\bot$\\
$\calC \gets \calC \cup x$\\
if $\Ans[x] \neq \undefined$\\
\nudge $(h_1, \ldots, h_{k}) \gets \HashOracle(x)$\\
Return $\Ans[x]$\\

>>>>

%\section{Proof of Theorem~\ref{thm:bf-correctness}}
%\label{sec:thm3_fp}
\begin{proof}[Theorem~\ref{thm:gbf-correctness}]
We use a game playing argument, please refer to Figures~\ref{fig:gbf-correctness-games1} and~\ref{gfig:bf-correctness-games2}. In game $\game{0}$, the $\Hash$ oracle performs lazy sampling of elements from $[m]$ to mimic a random oracle (RO). For every distinct query, $\Hash$ returns a random value sampled from $[m]$. It can be seen that, game $\game{0}$ exactly simulates the correctness game of $\setprim_{\mathrm{gbf}}$.  So, $\AdvCorrect{\setprim_{\mathrm{gbf}},r}{A} = \Prob{\game{0}(A) = 1}$.

Game $\game{1}$ is exactly same as game $\game{0}$ except the $\Qry$ call (inside the $\TestOracle$ oracle) is replaced by the code of $\Qry$.  Hence, $\Prob{\game{0}(A) = 1} = \Prob{\game{1}(A) = 1}$.

In game $\game{2}$, the $\Test$ oracle is altered to return the hash values~$h_1,h_2,\ldots, h_k$ in addition to the result of executing the code of $\Qry$.  As this only provides additional information to the adversary, $\Prob{\game{1}(A) = 1} \leq \Prob{\game{2}(A) = 1}$.

In $\game{3}$, we modify the $\HashOracle$ oracle so that on query~$\qry_x$ it returns all of the~$k$ values that previously would have required calls $\HashOracle(1,\qry_y),\HashOracle(2,\qry_y),\ldots,\HashOracle(k,\qry_y)$.  This results in adversary getting $(k-1)$ hash values ``for free'', as we charge the adversary only for a single query.  We alter the $\TestOracle$ oracle accordingly, so that it makes a single call $\Hash(\qry_x)$ rather than~$k$ such calls.

%tom here

@@

To summarize, 
\[
\AdvCorrect{\setprim_{\mathrm{gbf}},r}{A} \leq  {\dbinom{q_T + q_H}{r}} \left( (1-e^{-kn/m})^k + O(1/n) \right)^r\,.
\]
which is the bound claimed in the theorem statement.
\begin{figure}[tp]
\fpage{.95}{
\hpagessl{.5}{.5}
{
\underline{$\game{0}(A)$}\\
$S \getsr A$; $\calC \gets \emptyset$; $\err \gets 0$\\
$(\pubaux,\privaux) \getsr \Rep^{\HashOracle}(S)$\\
$\bot \getsr A^{\TestOracle,\HashOracle}(\pubaux)$\\
if $\err  < r$ then Return 0\\
Return 1\\

\oracle{$\TestOracle(\qry_x)$}\\
if $x \in \mathcal{C}$ then Return $\bot$\\
$\calC \gets \calC \cup x$\\
$a \gets \Qry^{\HashOracle,\HashOracle}(\pubaux,\privaux, x)$\\
if $a \neq \qry_x(S)$ then \\
\nudge $\err \gets \err + 1$\\
Return~$a$\\

\oracle{$\HashOracle(i,\qry_y)$}\\
$v \getsr [m]$\\
if $T[i,y] \neq \undefined$\\
\nudge $v \gets T[i,y]$\\
$T[i,y] \gets v$\\
Ret $v$
}
{
\underline{$\game{1}(A)$}\\
$S \getsr A$; $\calC \gets \emptyset$; $\err \gets 0$\\
$(\pubaux,\privaux) \getsr \Rep^{\HashOracle}(S)$\\
$\bot \getsr A^{\TestOracle,\HashOracle}(\pubaux)$\\
if $\err  < r$ then Return 0\\
Return 1\\

\oracle{$\TestOracle(\qry_x)$}\\
if $x \in \mathcal{C}$ then Return $\bot$\\
$\calC \gets \calC \cup x$; $M \gets\privaux$\\
for $j \in \{1,2,\ldots,k\}$\\
\nudge $h_j \gets \HashOracle(j, \qry_x)$\\
$x' \gets M[h_1] \xor M[h_2] \xor \ldots \xor M[h_k]$\\
if $x' \neq x$ then Return 0\\
$\err \gets \err + 1$\\
Return 1\\

\oracle{$\HashOracle(i,\qry_y)$}\\
$v \getsr [m]$\\
if $T[i,y] \neq \undefined$\\
\nudge $v \gets T[i,y]$\\
$T[i,y] \gets v$\\
Ret $v$
}
}
\fpage{.95}{
\hpagessl{.5}{.5}
{
\underline{$\game{2}(A)$}\\
$S \getsr A$; $\calC \gets \emptyset$; $\err \gets 0$\\
$(\pubaux,\privaux) \getsr \Rep^{\HashOracle}(S)$\\
$\bot \getsr A^{\TestOracle,\HashOracle}(\pubaux)$\\
if $\err  < r$ then Return 0\\
Return 1\\

\oracle{$\TestOracle(\qry_x)$}\\
if $x \in \mathcal{C}$ then Return $\bot$\\
$\calC \gets \calC \cup x$; $M \gets\privaux$\\
for $j \in \{1,2,\ldots,k\}$\\
\nudge $h_j \gets \HashOracle(j, \qry_x)$\\
$x' \gets M[h_1] \xor M[h_2] \xor \ldots \xor M[h_k]$\\
if $x' \neq x$ then Return $(0, (h_1, \ldots, h_j))$ \\
$\err \gets \err + 1$\\
Return $(1, (h_1, \ldots, h_{k}) )$ \\

\oracle{$\HashOracle(i,\qry_y)$}\\
$v \getsr [m]$\\
if $T[i,y] \neq \undefined$\\
\nudge $v \gets T[i,y]$\\
$T[i,y] \gets v$\\
Ret $v$
}
{
\underline{$\game{3}(A)$}\\
$S \getsr A$; $\calC \gets \emptyset$; $\err \gets 0$\\
$(\pubaux,\privaux) \getsr \Rep^{\HashOracle}(S)$\\
$\bot \getsr A^{\TestOracle,\HashOracle}(\pubaux)$\\
if $\err  < r$ then Return 0\\
Return 1\\

\oracle{$\TestOracle(\qry_x)$}\\
if $x \in \mathcal{C}$ then Return $\bot$\\
$\calC \gets \calC \cup x$; $M \gets\privaux$\\
$(h_1, \ldots, h_{k}) \gets \HashOracle(\qry_x)$\\
$x' \gets M[h_1] \xor M[h_2] \xor \ldots \xor M[h_k]$\\
if $x' \neq x$ then Return $(0, (h_1, \ldots, h_j))$ \\
$\err \gets \err + 1$\\
Return $(1, (h_1, \ldots, h_{k}) )$ \\

@@

\oracle{$\TestOracle(\qry_x)$}\\
if $x \in \mathcal{C}$ then Return $\bot$\\
$\calC \gets \calC \cup x$\\
if $\Ans[x] \neq \undefined$\\
\nudge $(h_1, \ldots, h_{k}) \gets \HashOracle(\qry_x)$\\
Return $\Ans[x]$\\

### 2016-09-30 notions.tex
fixing linebreaks and other cleaning
added note for Jon about RO usage in the correctness game

\section{Security Notions}
\label{sec:security-notions}
Following NY, we are interested in defining an adaptive (i.e.,
adversarial) notion of correctness.
In addition to correctness, we establish notions of privacy for
set-multiplicity data structures.

\fixme{Do we say that all notions can be extended to the ROM by giving
all all algorithms to a RO~$H$?  Is this true for the SS-privacy
notion?  (It seems to make sense elsewhere.)} \jnote{I think there are subtleties for the SS notion.}

@@

Formally, our definition is specified by an experiment called $\ExpCorrect{\setprim,r}{A}$
given in Figure~\ref{fig:correctness}.
Following an initialization step,
the experiment begins by having the attacker $A$ outputs data $S \in \univ$.
Then, $\Rep(S)$ is run to generate a representation $(\pubaux,\privaux)$ for that data.
%\jnote{I thought we were going to let
%the adversary choose~$S$?} \tsnote{Email discussion. At this point,
%I'm happy just making~$S$ part of the experiment ``name'', the
%way~$\distr{}{}$ is now.  The distribution seems not to matter for
%correctness, at least for the schemes we consider.} \jnote{If instead we choose $S$ from ${\cal D}$, then
%is it clear we want to give $S$ to~$A$?} \tsnote{For \emph{correctness},
%yes, if for no other reason than to allow~$A$ to know when it asking
%a pointless query.  But also it will make no difference to the
%provable correctness of the constructions we consider.}
%\jnote{OK, I think I would just change the definitions so that the attacker
%chooses $S$.}
%(Unless stated otherwise, we assume security holds for all distributions and thus for all sets $S$.)
The adversary~$A$ is given~$\pubaux$, and is also
provided with access to an oracle~$\TestOracle$ that, on input a query~$\qry \in \calQ$,
returns $\Qry(\pubaux,\privaux,\qry)$ to $A$ and also increments
a counter if this result is incorrect (and if $\qry$ is new).  The adversary succeeds if it
manages to cause at least~$r>0$ such errors among its queries.
The definition can be lifted to the random-oracle model by providing
all algorithms (namely, $\Rep,\Qry$, and the adversary~$A$) with access to the
random oracle.

@@

We next show that any canonical data structure in which~$F$ is a pseudorandom function is
semantically secure with respect to leakage consisting of the size of the set.
\jnote{Need notation for the advantage in the PRF experiment.}

>>>>

\section{Security Notions}
\label{sec:security-notions}
Following NY, we are interested in defining an adaptive (i.e.,
adversarial) notion of correctness.
In addition to correctness, we establish notions of privacy for data structures.

%\fixme{Do we say that all notions can be extended to the ROM by giving
%all all algorithms to a RO~$H$?  Is this true for the SS-privacy
%notion?  (It seems to make sense elsewhere.)} \jnote{I think there are subtleties for the SS notion.}

@@

Formally, our definition is specified by an experiment called $\ExpCorrect{\setprim,r}{A}$
given in Figure~\ref{fig:correctness}.
Following an initialization step,
the experiment begins by having the attacker $A$ outputs data $S \in \univ$.
Then, $\Rep(S)$ is run to generate a representation $(\pubaux,\privaux)$ for that data.
%\jnote{I thought we were going to let
%the adversary choose~$S$?} \tsnote{Email discussion. At this point,
%I'm happy just making~$S$ part of the experiment ``name'', the
%way~$\distr{}{}$ is now.  The distribution seems not to matter for
%correctness, at least for the schemes we consider.} \jnote{If instead we choose $S$ from ${\cal D}$, then
%is it clear we want to give $S$ to~$A$?} \tsnote{For \emph{correctness},
%yes, if for no other reason than to allow~$A$ to know when it asking
%a pointless query.  But also it will make no difference to the
%provable correctness of the constructions we consider.}
%\jnote{OK, I think I would just change the definitions so that the attacker
%chooses $S$.}
%(Unless stated otherwise, we assume security holds for all distributions and thus for all sets $S$.)
The adversary~$A$ is given~$\pubaux$, and is also
provided with access to an oracle~$\TestOracle$ that, on input a query~$\qry \in \calQ$,
returns $\Qry(\pubaux,\privaux,\qry)$ to $A$ and also increments
a counter if this result is incorrect (and if $\qry$ is new).  The adversary succeeds if it
manages to cause at least~$r>0$ such errors among its queries.
The definition can be lifted to the random-oracle model by providing
all algorithms (namely, $\Rep,\Qry$, and the adversary~$A$) with access to the
random oracle. \fixme{I think we should *not* allow $S$ to depend on
  the RO.  That's like letting $S$ depend on $\pub$ in the standard
  model, but $\pub$ hasn't been fixed yet.  }

@@

We next show that any canonical data structure in which~$F$ is a pseudorandom function is
semantically secure with respect to leakage consisting of the size of the set.
\jnote{Need notation for the advantage in the PRF
  experiment.}\tsnote{Currently typeset in an appendix}
